### 2019-09-01 paper/paper.tex
First draft of discussion and conclusion.

  \includegraphics[width=4in]{../figures/reference-geometry.png}

@@

The parameters of the bicycles can be distilled into open loop eigenvalues for
a clearer understanding of the dynamics, shown in
Figure~\ref{fig:optimal-eigenvalues}. The 3 and 9 design speed have a simlar
eigenvalue pattern as well as the 5 and 7.

%
\begin{figure}
  \centering
  \includegraphics[width=6in]{../figures/optimal-eigenvalues.png}
  \label{fig:optimal-eigenvalues}
  \caption{Real (solid) and imaginary (dashed) parts of the open-loop eigenvlues plotted versus
    travel speed. The vertical dashed black line indicates the design speed.}
\end{figure}

\section{Discussion and Conclusion}
%
- need constraints to keep rider out of wheels
- need more realistic constraints for the frame mass and inertia based on space
frame
- need constraints of rear frame that force it to span from rear wheel to
person to head tube
\section{Reproducibility}
%
All of the source code, data, and documents needed to reproduce the presented
results and this paper can be found at the repository hosted at
\url{https://github.com/moorepants/BMD2019}.

>>>>

  \includegraphics[width=3in]{../figures/reference-geometry.png}

@@

The parameters of the bicycles can be distilled into open loop eigenvalues for
a clearer understanding of the dynamics, shown in
Figure~\ref{fig:optimal-eigenvalues}. The 3 and 9 design speed have a simlar
eigenvalue pattern as well as the 5 and 7. The 7~\si{\meter\per\second} design
is self-stable at speeds greater than 1.2~\si{\meter\per\second} but the other
three designs are not self-stable at any travel speed from
\SIrange{0}{10}{\meter\per\second}. Both the 5 and 7 designs have a weave mode
that increases in frequency rapidly with speed. The weave frequency of the 3
m/s design is higher than the reference design and present at all speeds.
%
\begin{figure}
  \centering
  \includegraphics[width=6in]{../figures/optimal-eigenvalues.png}
  \label{fig:optimal-eigenvalues}
  \caption{Real (solid) and imaginary (dashed) parts of the open-loop eigenvlues plotted versus
    travel speed. The vertical dashed black line indicates the design speed.}
\end{figure}

\section{Discussion and Conclusion}
%
We have demonstrated the ability to find optimal parameter values of the linear
Whipple-Carvallo bicycle model under constraints that enforce a physically
realizable bicycle with an objective of improving lateral handling qualities.
We showcase four optimal bicycle designs for a range of target travel speeds.
The resulting bicycles are similar to the familiar and popular bicycle design
but have some oddities: very large size relative to the person, large negative
trail, large positive trail, minimal steer inertia, recumbent rider
orientation, and both very low and high rider mass center locations. Three of
the four bicycles are not open-loop self stable for any speed up to
10~\si{\meter\per\second} and the weave model frequencies are significantly
larger than the reference bicycle but all bicycles are controllable and have a
minimal HQM as defined in~\cite{Hess2012}.

The bicycles are reasonably physically realizable but some additional
constraints could be introduced to further improve this. In the
5~\si{\meter\per\second} design the person's body overlaps the wheels, which
would be almost impossible to realize. A constraint that ensures the torso
cannot occupy the same space as the wheels would solve this. The masses of the
front and rear frames are low with respect to the geometrical spread a steel
space frame would have to occupy. The frames also need to be able to span the
space between the respecitve wheel, mass center of the frame, and the steer
axis and for the rear frame span to the rider's support locations. We currently
only expliclty deal with spanning the space between the mass center of the
frame and the respective wheel. Another more restricting appraoch would be to
specify a generic geometric structure for the front and rear frames. If done,
maximal stress and deflections of the frames under load could also be
minimized.

Each optimizal solution requires approximately 12 hours of computation time on
a high end consumer desktop machine running on a single thread. The number of
iterations are typically in the hundreds of thousands for convergence. There
are many avenues for speeding this up that could likely result in solutions in
one or two hours on the same machine but this is still slow to be particualrly
pleasant to utlizie in the process of designing a bicycle. Furthermore, the
time required to translate the resulting parameters in to an actual bicycle
design complete with structural destails is extremely time consuming.
Never-the-less, the method shows promise for optimizing an entire vehicle for
optimal dynamics. This method can be applied to a whole host of human operated
vehicles opening up many new designs, but as with any optimization it only
captures a very small set of the variables that a designer has to take into
account for a vehicle.

\section{Reproducibility}
%
All of the source code, data, and documents needed to reproduce the presented
results and this paper can be found at the repository hosted at
\url{https://github.com/moorepants/BMD2019}.
